Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-23 manual/projectrapport.tex

@@

>>>>

\section{Compiling multi-platform}
A lot of obstacles were tackled while getting the project to work an Windows. When building with GTest on Windows you need to use the \texttt{-std=gnu++11} flag instead of the standard \texttt{-std=c++11} flag, because we need the GNU extensions to correctly link everything.

All standard c++11 \textit{to string} functionality in Cygwin is not supported \cite{cygwin_tostring} (MinGW32 doesn't support this either). With basic \textit{to string} functionality we mean the functions that are listed here \cite{c++11_tostring} and under the 'See also' section. The problem seems to be a library called Newlib \cite{newlib} that doesn't provide crucial functions.

Mac OSX needs the libc++ library to compile all C++11 features on.

@@

  \bibitem{c++11_tostring} \url{http://en.cppreference.com/w/cpp/string/basic_string/to_string}

  \bibitem{cygwin_tostring} \url{https://cygwin.com/ml/cygwin/2015-01/msg00245.html}

  \bibitem{newlib} \url{https://sourceware.org/newlib/}
